---
title: "Example of Rmarkdown in Tiddlywiki"
always_allow_html: true
output: 
  rtiddlywiki::tiddler_document:
    use_bookdown: true
    number_sections: false
    tags: ["Rmarkdown"]
    overwrite: true
  html_document: default
vignette: >
  %\VignetteIndexEntry{rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Here we show to create a tiddler with interactive figures from Rmarkdown. The source of Rmarkdown can be found from [github](https://github.com/byzheng/rtiddlywiki/blob/main/examples/rmarkdown-example.Rmd).

```{r load-package}
# Load the required package
library(rtiddlywiki)
```


# Leaflet package

[Leaflet](https://leafletjs.com/) is one of the most popular open-source JavaScript libraries for interactive maps. R [leaflet](https://rstudio.github.io/leaflet/) package makes it easy to integrate and control Leaflet maps in R. All examples below come from [leaflet website](https://rstudio.github.io/leaflet/).

```{r leaflet-map, results='asis'}


library(leaflet)
m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=174.768, lat=-36.852, popup="The birthplace of R")
m %>% 
    tw_widget()
```

## Markers

```{r leaflet-markers}
data(quakes)

# Show first 20 rows from the `quakes` dataset
leaflet(data = quakes[1:20,]) %>% addTiles() %>%
  addMarkers(~long, ~lat, popup = ~as.character(mag), label = ~as.character(mag)) %>% 
    tw_widget()
```

```{r leaflet-curcle-markers}
df <- sp::SpatialPointsDataFrame(
  cbind(
    (runif(20) - .5) * 10 - 90.620130,  # lng
    (runif(20) - .5) * 3.8 + 25.638077  # lat
  ),
  data.frame(type = factor(
    ifelse(runif(20) > 0.75, "pirate", "ship"),
    c("ship", "pirate")
  ))
)
leaflet(df) %>% addTiles() %>% addCircleMarkers() %>% tw_widget()

```


## Static images

```{r static-images-1}

library(ggplot2)
cars |> 
    ggplot() +
    geom_point(aes(speed, dist))
```

```{r static-images-2}

cars |> 
    ggplot() +
    geom_point(aes(speed, dist)) +
    theme_bw()
```
